Positive Relationship between a Country's Employment Rate and Permanent Immigrant Inflows

### 2023-04-17 outputs/paper/paper.qmd
commit

---
title: "Positive Relationship between a Country's Employment Rate and Permanent Immigrant Inflows"
subtitle: "An Analysis of United States, Canada, United Kingdom, Australia, and Japan"
author: 
  - Jenny Shen
thanks: "Code and data are available at: https://github.com/jennyshen-playground/analysis_of_employment_rate_perminant_immigrant_inflows.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "This paper explores the relationship between a country's employment rate and its ability to attract and retain permanent immigrants. Using a linear regression analysis, we examine five countries with relatively high immigration numbers: United States, Canada, United Kingdom, Australia, and Japan from 2008 to 2018. We drawn data  from the OECD website, with a focus on the percentage of the working-age population. These findings matter as they can influence permanent immigrant inflows and guide governments in developing policies to attract and retain permanent immigrants.The rise of employment rate can enhance economic development, and also associates with increased number of permanent immigrants inflow. This suggests that improving employment rate leads to better immigration that generate significant economic and social benefits for a country."
number-sections: true
bibliography: references.bib
---

@@

In this paper, we will examine the relationship between a country's employment rate and permanent immigrant inflows through a linear regression analysis, The estimand here that we're trying to estimate is the correlation of employment rate and permanent immigrants inflows. Specifically, we will focus Canada, which has relatively high immigration number. We will draw data from the OECD website. Our respondents of interest are the percentage of the working-age population, as they represent the potential labor force and have a significant impact on a country's economic growth and development.

@@

```{r}
#| include: false
#| warning: false
#| message: false
#| 
#### Initialize quarto workspace by reading csv's ####
library(tidyverse)
library(here)

permanent_immigrant <- read_csv(here::here("inputs/data/permanent_immigrant_inflows_cleaned.csv"))
employment_rate <- read_csv(here::here("inputs/data/employment_rate_cleaned.csv"))
merged_data <- read_csv(here::here("inputs/data/merged_data.csv"))
```

```{r}

#| label: fig-1
#| fig-cap: A graph detailing that the overall increase in the permenant immigration inflow from 2008 to 2019 is from...
#|  mean highest education level percentage of women over a 20 year period from 2000 to 2021 is from 13.0 to 13.7.
#| echo: false
#| warning: false

@@

>>>>

---
title: "Positive Relationship between a Country's Employment Rate and Permanent Immigrant Inflows"
subtitle: "An Analysis of Canada's Employment Rate and Permanent Immigrant Inflows"
author: 
  - Jenny Shen
thanks: "Code and data are available at: https://github.com/jennyshen-playground/analysis_of_employment_rate_perminant_immigrant_inflows.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "This paper explores the relationship between a country's employment rate and its ability to attract and retain permanent immigrants. Using a linear regression analysis, we examine five countries with relatively high immigration numbers: United States, Canada, United Kingdom, Australia, and Japan from 2008 to 2018. We drawn data  from the OECD website, with a focus on the percentage of the working-age population. These findings matter as they can influence permanent immigrant inflows and guide governments in developing policies to attract and retain permanent immigrants.The rise of employment rate can enhance economic development, and also associates with increased number of permanent immigrants inflow. This suggests that improving employment rate leads to better immigration that generate significant economic and social benefits for a country."
number-sections: true
bibliography: references.bib
---

@@

In this paper, we will examine the relationship between a country's employment rate and permanent immigrant inflows through a linear regression analysis, The estimand here is how employment rate and immigrants inflows are related. Specifically, we will focus Canada, which has relatively high immigration number. We will draw data from the OECD website. Our respondents of interest are the percentage of the working-age population, as they represent the potential labor force and have a significant impact on a country's economic growth and development.

@@

```{r}
#| include: false
#| warning: false
#| message: false

#### Initialize quarto workspace by reading csv's ####
library(tidyverse)
library(here)

permanent_immigrant_cleaned <- read_csv(here::here("inputs/data/permanent_immigrant_inflows_cleaned.csv"))
employment_rate_cleaned <- read_csv(here::here("inputs/data/employment_rate_cleaned.csv"))
total_population_cleaned <- read_csv(here::here("inputs/data/total_population_cleaned.csv"))
merged_data <- read_csv(here::here("inputs/data/merged_data.csv"))

## Permanent Immigrants Inflows Rate from 2009 to 2019

```{r}
#| label: fig-1
#| fig-cap: A graph detailing that the overall increase in Canada's permenant immigration inflow from 2009 to 2019 which is from 249292 to 341173.
#| echo: false
#| warning: false

merged_data |>
  mutate(Permanent_Inflows_Rate = (Permanent_Inflows / Population) * 100) |>
  group_by(Year) |>
  summarize(Permanent_Inflows_Rate = sum(Permanent_Inflows_Rate, na.rm = TRUE)) |>
  ggplot(aes(x = Year, y = Permanent_Inflows_Rate)) +
  geom_line(group = 1, color = "red") +
  scale_x_continuous(breaks = seq(2009, 2019, by = 1), labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019")) +
  theme_bw() +
  labs(
    title = "Permanent Immigrants Inflows Rate from 2009 to 2019",
    x = "Year",
    y = "Permanent Immigrants Inflows Rate" 
  )

\
\## Employment Rate from 2009 to 2019

```{r}
#| label: fig-2
#| fig-cap: "A graph detailing that the overall increase in Canada's permenant immigration inflow from 2009 to 2019 which is from 249292 to 341173."
#| echo: false
#| warning: false

merged_data |>
  group_by(Year) |>
  summarize(Employment_Rate = sum(Employment_Rate, na.rm = TRUE)) |>
  ggplot(aes(x = Year, y = Employment_Rate)) +
  geom_line(group = 1, color = "blue") +
  scale_x_continuous(breaks = seq(2009, 2019, by = 1), labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019")) +
  theme_bw() +
  labs(
    title = "Employment Rate in Canada from 2009 to 2019",
    x = "Year",
    y = "Employment Rate" 
  )

@@

```{r}
#| echo: false
#| warning: false
#| label: tab-1
#| tab-cap: "A summary table of two linear regression models"

library(modelsummary)

merged_data <-
  merged_data |>
  mutate(Permanent_Inflows_Rate = (Permanent_Inflows / Population) * 100) |>
  mutate(Centred_Employment_Rate = Employment_Rate - mean(merged_data$Employment_Rate))

merged_data_centered_model <-
  lm(
    Permanent_Inflows_Rate ~ Employment_Rate,
    data = merged_data
  )

modelsummary::modelsummary(
  list("Employment Rate" = merged_data_centered_model),
  fmt = 2
)

```{r}
#| label: fig-3
#| fig-cap: "A graph detailing that the overall increase in Canada's permenant immigration inflow from 2009 to 2019 which is from 249292 to 341173."
#| echo: false
#| warning: false

merged_data <- merged_data %>%
  mutate(Permanent_Inflows_Rate = Permanent_Inflows / Population * 100)

  ggplot(merged_data, aes(x = Employment_Rate, y = Permanent_Inflows_Rate)) +
  geom_point(alpha = 0.5) +
  geom_smooth(
    method = "lm",
    se = TRUE,
    color = "black",
    linetype = "dashed",
    formula = "y ~ x"
  ) +
  labs(
    x = "Employment Rate (percentage)",
    y = "Permanent Inflows Rate (percentage)"
  ) +
  theme_classic()

$$
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
$$ {#eq-bayes}

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details]

## Model set-up

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
